A sheaf--function dictionary for algebraic tori over local fields

### 2013-09-24 shanghai.tex
Working on a diagram in Section 6

\begin{proof}
Set $H_m \ceq H\times_G(G\times G)$, write $f_m : H_m \to G \times G$ for the pullback of $f$ to $H_m$, and let $A$ and $A_m$ be the kernels of $f$ and $f_m$ respectively.  Consider the diagram of Lemma~\ref{lemma:finite-pull-back}:
\[
\begin{tikzcd}[column sep=40]
V & \Aut(V) & \arrow[swap]{l}{\psi} A \arrow[hook]{r} & H \arrow{r}{f} &  G\\
  &  & \arrow[dashed]{ul}{\psi_m} \arrow[swap]{u}{(m_f)\vert_{A_m}} A_m \arrow[hook]{r}
  & \arrow[swap]{u}{m_f} H_m \arrow{r}{f_m} & \arrow{u}{m} G\times G.
\end{tikzcd}
\]
We have $(f,\psi) \boxtimes (f,\psi) = (f\times f, \psi\otimes \psi)$.
Since $f\circ m_H = m \circ (f\times f)$, the universal property of pull-back gives
a unique $\theta : H\times H \to H_m$ making the following commute.
\[
\begin{tikzcd}[row sep=20,column sep=10]
\ & V \arrow{dd}{T} && \Aut(V) && \arrow{dl} \arrow[swap]{ll}{\psi_m} A_m \arrow[hook]{rr}
&& \arrow[swap]{ld}{m_f} H_m \arrow{rr}{f_m} && \arrow[equal]{dd} \arrow{ld}{m} G\times G\\
 && && \arrow{ul}{\psi} A  \arrow[hook]{rr} && H  \arrow[swap, pos=0.8]{rr}{f} && G  & \\
& V\otimes V && \Aut(V)
&& \arrow[swap]{ll}{\psi \otimes \psi} \arrow[swap,pos=0.8]{uu}{\theta\vert_{A\times A}} A\times A \arrow[hook]{rr}
&& \arrow[swap,pos=0.8]{uu}{\theta} \arrow{ul}{m_H} H\times H \arrow{rr}{f\times f} && G\times G
\end{tikzcd}
\]
Choose a basis $\{ v \}$ for $V$; then $\{ v\otimes v \}$ is a basis for $V\otimes V$.
Define $T : V \to V\otimes V$ by $T(v) \ceq v\otimes v$. Then the lower part of this
diagram defines a weak isomorphism $(\theta,T): m^*(f,\psi) \to (f,\psi)\boxtimes (f,\psi)$  in $C_1(G)$.

>>>>

\begin{proof}
Set $H_m \ceq H\times_G(G\times G)$, write $f_m : H_m \to G \times G$ for the pullback of $f$ to $H_m$, and let $A$ and $A_m$ be the kernels of $f$ and $f_m$ respectively.  Consider the diagram of Lemma~\ref{lemma:finite-pull-back}:
\[
\begin{tikzcd}[column sep=40]
V & \Aut(V) & \arrow[swap]{l}{\psi} A \arrow[hook]{r} & H \arrow{r}{f} &  G\\
  &  & \arrow[dashed]{ul}{\psi_m} \arrow[swap]{u}{(m_f)\vert_{A_m}} A_m \arrow[hook]{r}
  & \arrow[swap]{u}{m_f} H_m \arrow{r}{f_m} & \arrow{u}{m} G\times G.
\end{tikzcd}
\]
We have $(f,\psi) \boxtimes (f,\psi) = (f\times f, \psi\otimes \psi)$.
Since $f\circ m_H = m \circ (f\times f)$, the universal property of pull-back gives
a unique $\theta : H\times H \to H_m$ making the following commute.
\[
\begin{tikzcd}[row sep=20,column sep=10]
\ & V \arrow{dd}{T} && \Aut(V) && A \arrow[hook]{rr} \arrow[swap]{ll}{\psi} &&  H \arrow{rr}{f} && G\\
 && && \arrow{ul}{\psi_m} A_m  \arrow[hook]{rr} \arrow{ur} && H_m \arrow[pos=0.3]{ur}{m_f} \arrow[swap, pos=0.8]{rr}{f_m}
 && G \times G \arrow[equal]{dr} \arrow[pos=0.42]{ur}{m} & \\
& V\otimes V && \Aut(V) && \arrow[swap]{ll}{\psi \otimes \psi} \arrow[dashed,swap,pos=0.3]{ul}{\theta\vert_{A\times A}} A\times A \arrow[hook]{rr}
&& \arrow[dashed,swap]{ul}{\theta} \arrow[crossing over,swap,pos=0.7]{uu}{m_H} H\times H \arrow{rr}{f\times f} && G\times G
\end{tikzcd}
\]
Choose a basis $\{ v \}$ for $V$; then $\{ v\otimes v \}$ is a basis for $V\otimes V$.
Define $T : V \to V\otimes V$ by $T(v) \ceq v\otimes v$. Then the lower part of this
diagram defines a weak isomorphism $(\theta,T): m^*(f,\psi) \to (f,\psi)\boxtimes (f,\psi)$  in $C_1(G)$.
